---
title: "R Notebook"
output: html_notebook
---

Part 1
```{r}
stock_prices <- c(23, 27, 23, 21, 34, 24, 25, 30, 37, 30)
day_of_week <- rep(c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday'), times = 2)
day_of_week
```
Factor's are the same as character vectors but R assigns them as numbers
```{r}
day_of_week_factor <- as.factor(day_of_week)
day_of_week_factor
```
Created a vector called named_stock_prices, which is stock prices, named with days of the week.

```{r}
named_stock_prices <- stock_prices
names(named_stock_prices) <- c(day_of_week)
head(named_stock_prices)
```


Make a data frame called stock_data with the stock price and day of the week information in it, and View the result. 
This will assign the name stock_prices to stock_prices and day_of_week to day_of_week
```{r}
stock_data <- data.frame(stock_prices = stock_prices, day_of_week = day_of_week)
stock_data
```


Make a matrix called stock_matrix with 2 columns and 5 rows, so that the stock prices for one week are the first column, and the stock prices for the second week are the second column.
```{r}
stock_matrix <- matrix(stock_data$stock_prices, nrow = 5, byrow = FALSE)
stock_matrix
```


Make a list called stock_list with named elements, that has the individual vectors of stock_prices and day_of_week along with the matrix you made in question 4.
```{r}
stock_list <- list(stock_prices = stock_prices, day_of_week = day_of_week, stock_matrix = stock_matrix)
stock_list
```


Part 2
In this part of the homework you will practice selecting elements from vectors, data frames, matrices and lists.
Select the 4th, 5th and 6th stock prices from stock_prices. Alternative stock_prices[c(4, 5, 6)]
```{r}
stock_prices[4:6]
```


Select the stock prices greater than 30 from stock_prices.
```{r}
stock_prices[stock_prices > 30]
```


Select the day_of_week column from the stock_data data frame.
```{r}
stock_data$day_of_week
```

Select the rows of the stock_data data frame where the stock_prices is less than 25.  Alternative subset(stock_data, stock_prices <25)
```{r}
stock_data[stock_data$stock_prices < 25, ]
```


Select the 1st column of the matrix
```{r}
stock_matrix[ , 1]
```


Select the 3rd row of the matrix
```{r}
stock_matrix[3, ]
```

Select the 3rd element in the 1st row of the matrix
```{r}
dim(stock_matrix)
```
```{r}
stock_matrix[1, 3]
```


Select the matrix stock_matrix from stock_list.
Need doube bracket to show you the actual matrix object
Single brack will only return the element as a list!
```{r}
stock_list[[3]]
```


3 Extension
Download the tidyquant library.
```{r}
install.packages("tidyquant")
```

Use it to get stock prices from a company of your choice from the current year. You’ll need to look up the help file to do this.
```{r}
library(tidyquant)
```

```{r}
google_prices <- tq_get("GOOGL", get = "stock.prices", from = "2019-01-01")
google_prices$open <- NULL
google_prices$high <- NULL
google_prices$low <- NULL
google_prices$volume <- NULL
google_prices$adjusted <- NULL

```



Edit the data frame so only columns are date and closing.
Subset to find the rows where closing price is higher than average.




