Anscombe’s quartet exists as a packaged list in R. Run data(anscombe) and then have a look at the str() of the  list. Find the names of the eight variables.
```{r}
data(anscombe)
str(anscombe)
summary(anscombe)
```

```{r}
print(paste("The names of the eight variables are: x1, x2, x3, x4, y1, y2, y3 and y4"))
```

Calculate the mean() and sample var() of each of the eight variables in the dataframe.
```{r}
attach(anscombe)
mean_values <- sapply(anscombe,
                     FUN = mean)

variance_values <- sapply(anscombe,
                          FUN = var)

median_values <- sapply(anscombe, 
                        FUN  = median)

summary_abscombe <- matrix(data = c(mean_values, 
                                    variance_values, 
                                    median_values), 
                  ncol = 8, 
                  byrow = TRUE)
colnames(summary_abscombe) <- c("x1", "x2", "x3", "x4", "y1", "y2", "y3", "y4")
rownames(summary_abscombe) <- c("Mean", "Variance", "Median")
summary_abscombe

```

Interpret your results from above. How similar do you think the eight datasets are purely on the basis of mean() and  var()?

The x data sets have the same mean and variance, 
The y data sets also have similar mean and variance.


Create box plots for the eight data sets and interpret what you see. Perhaps calculate IQR() and skewness() for each set. Should you change your conclusions from above?
```{r}
boxplot(x1, 
        horizontal = TRUE, 
        col = rgb(1, 0, 0, 
        alpha = 1/2))
boxplot(x2, 
        horizontal = TRUE, 
        col = rgb(0.3, 0.3, 0.3, 
        alpha = 1/2))
boxplot(x3, 
        horizontal = TRUE, 
        col = rgb(0, 1, 0, 
        alpha = 1/2))
boxplot(x4, 
        horizontal = TRUE, 
        col = rgb(0, 0, 1, 
        alpha = 1/2))

```
```{r}
boxplot(y1, 
        horizontal = TRUE, 
        col = rgb(1, 0, 0, 
        alpha = 1/2))
boxplot(y2, 
        horizontal = TRUE, 
        col = rgb(0.3, 0.3, 0.3, 
        alpha = 1/2))
boxplot(y3, 
        horizontal = TRUE, 
        col = rgb(0, 1, 0, 
        alpha = 1/2))
boxplot(y4, 
        horizontal = TRUE, 
        col = rgb(0, 0, 1, 
        alpha = 1/2))
```

Anscombe intended his eight sets to be interpreted as four sets of (x,y) data: (x1,y1), (x2,y2), (x3,y3) and (x4,y4). Plot y1-vs-x1, y2-vs-x2, y3-vs-x3 and y4-vs-x4 using the plot() function and comment on what you observe.
```{r}
plot(x1, y1, col = rgb(1, 0, 0, alpha = 1/2), 
     xlim = c(0, 20),
     ylim = c(0, 20),
     xlab = "x1", 
     ylab = "y1")
plot(x2, y2, col = rgb(0, 1, 0, alpha = 1/2), 
     xlim = c(0, 20),
     ylim = c(0, 20),
     xlab = "x2", 
     ylab = "y2")
plot(x3, y3, col = rgb(0, 0, 1, alpha = 1/2), 
     xlim = c(0, 20),
     ylim = c(0, 20),
     xlab = "x3", 
     ylab = "y3")
plot(x4, y4, col = rgb(0.5, 0.5, 0.5, alpha = 1/2), 
     xlim = c(0, 20),
     ylim = c(0, 20),
     xlab = "x4", 
     ylab = "y4")
```


2.2 Extension - correlation
Calculate the correlation coefficient for each (x,y) pair of variables using the cor() function. Interpret the results you obtain: in particular, given what we observed above, do you think we’re justified in saying that similar correlation coefficients indicate similar linear trends?

```{r}
correlation_x1_y1 <- cor(x1, y1)
correlation_x2_y2 <- cor(x2, y2)
correlation_x3_y3 <- cor(x3, y3)
correlation_x4_y4 <- cor(x4, y4)
print(paste("The correlation between x1 and y1 is:", correlation_x1_y1, 
            "The correlation between x2 and y2 is:", correlation_x2_y2,
            "The correlation between x3 and y3 is:", correlation_x3_y3,
            "The correlation between x4 and y4 is:", correlation_x4_y4))
```

From the plot we can see a similar positive trend between the 4 sets of data. 
We can say that there is strong correlation between all the data points which follows a similar linear trend
